Modern Graph Generators: A Survey

### 2018-09-11 generators_LinkedData.tex
Minor corrections

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}. The \texttt{LUBM} benchmark also provides 14 test queries. The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties). The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploting classical linear congruential generator, LCG, of numbers). In particular, data generated by the tool are exactly repeatable with respect to universities (assigning them zero-based indexes, i.e., the first university is named University0 and so on).  The generator allows a user to specify the seed for random number generation, the number of universities, and the starting index of the universities.

An extension of \texttt{LUBM}, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase. The authors present a probabilistic model that, given representative data of some domain, can capture the properties of the data and generate synthetic data that has similar properties. A Monte Carlo algorithm is used to generate synthetic data. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes and 80 properties. 12 test queries were designed for  the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

@@

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, models an e-commerce domain where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write~\cite{Bizer09theberlin}.
The benchmark comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product. The data generator supports creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 ? 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 ? 1)$) etc. BSBM can output two representations -- an RDF representation and a purely relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results with the performance of traditional RDBMSs.

@@

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}, the Barton Libraries Dataset~\cite{barton-benchmark}
WordNet~\cite{Miller:1995:WLD:219717.219748} etc.) is provided in paper~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$. The type system is extracted from the data set looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset along with a desired level of structuredness and size (smaller than the size of the original data), and uses the input dataset as a seed to produce a subset of the original data with the indicated size and structuredness. In addition they show that structuredness and size mutually influence each other.

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that were issued by humans and applications
against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous (e.g., DBpedia version 3.6, for example, contains 289,016 classes of which 275 classes belong
to the DBpedia ontology) and various datatypes and object references of different types are
used in property values. Hence, they propose a generic SPARQL benchmark creation methodology based on: a flexible data generation mimicking an input data source, query-log mining, clustering, and SPARQL feature analysis. The proposed dataset creation process starts with an input dataset. Datasets of multiple size of the original data are created by duplicating all triples and changing their namespaces.  For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset. The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity. The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, which cover most commonly used SPARQL features and are used to generate the actual benchmark queries by parametrization.

@@

\paragraph{Geographica} The Geographica benchmark \footnote{\url{http://geographica.di.uoa.gr/}} has been designed target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions \texttt{GeoSPARQL}~\cite{battle2012enabling} and \texttt{stSPARQL}~\cite{koubarakis2010modeling}. The benchmark involves (1) a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and (2) a synthetic workload. In the former case they further distinguish (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark introduce two classes of query features -- structural and data-driven -- and perform an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features. The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that they are not sufficiently diverse to test the strengths and weaknesses of different physical design choices employed by RDF systems. The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which computes the structural and data-driven features of the generated data and workload. For the study in the paper the authors generated 12,500 test queries from 125 query templates.

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template, and generates a set of synthetic datasets with similar characteristic, the required size scaling factor $s$ and the (node) degree scaling factor $d$. A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics -- dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity -- are utilized for this purpose. A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data. The benchmark project \texttt{FEASIBLE}~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
size from the input set of queries.

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade, benchmarks for graph and RDF databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark considers a media or a publishing organization that deals with large volume of streaming content, namely news, articles or  ``media assets''. This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets. The data generator models three types of relations in produced synthetic data: (1) clustering of data, (2) correlations of entities, and (3) random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix, querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes. The LDBC designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).

\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}. The generator is designed to receive a vocabulary as an input  and supports two statistical distribution techniques for generating entities: Gaussian distribution and Zipf's power-law distribution. \texttt{LinkGen} can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statement by assigning invalid domain and creating instances with no type information. The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets. The datasets can be generated in any of of two modes: on-disk and streaming.

>>>>

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}. The LUBM benchmark also provides 14 test queries. The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties). The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploiting classical linear congruential generator, LCG, of numbers). In particular, data generated by the tool are exactly repeatable with respect to universities (assigning them zero-based indexes, i.e., the first university is named University0 and so on).  The generator allows a user to specify the seed for random number generation, the number of universities, and the starting index of the universities.

An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase. The authors present a probabilistic model that, given representative data of some domain, can capture the properties of the data and generate synthetic data that has similar properties. A Monte Carlo algorithm is used to generate synthetic data. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes and 80 properties. 12 test queries were designed for  the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

@@

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, models an e-commerce domain where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write~\cite{Bizer09theberlin}.
The benchmark comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product. The data generator supports creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc. BSBM can output two representations -- an RDF representation and a purely relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results with the performance of traditional RDBMSs.

@@

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}, the Barton Libraries Dataset~\cite{barton-benchmark} or
WordNet~\cite{Miller:1995:WLD:219717.219748}) is provided in paper~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$. The type system is extracted from the data set by looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset along with a desired level of structuredness and size (smaller than the size of the original data), and uses the input dataset as a seed to produce a subset of the original data with the indicated size and structuredness. In addition they show that structuredness and size mutually influence each other.

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that were issued by humans and applications
against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous (e.g., DBpedia version 3.6, for example, contains 289,016 classes of which 275 classes belong
to the DBpedia ontology) and various datatypes and object references of different types are
used in property values. Hence, they propose a generic SPARQL benchmark creation methodology based on a flexible data generation mimicking an input data source, query-log mining, clustering, and SPARQL feature analysis. The proposed dataset creation process starts with an input dataset. Datasets of multiple size of the original data are created by duplicating all triples and changing their namespaces.  For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset. The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity. The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, which cover most commonly used SPARQL features and are used to generate the actual benchmark queries by parametrization.

@@

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark introduces two classes of query features -- structural and data-driven -- and performs an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features. The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that they are not sufficiently diverse to test the strengths and weaknesses of different physical design choices employed by RDF systems. The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which computes the structural and data-driven features of the generated data and workload. For the study in the paper the authors generated 12,500 test queries from 125 query templates.

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template and generates a set of synthetic datasets with similar characteristics, required size scaling factor $s$ and (node) degree scaling factor $d$. A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity. A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data. The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
size from the input set of queries.

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade benchmarks for graph and RDF databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark considers a media or a publishing organization that deals with large volume of streaming content, namely news, articles or  ``media assets''. This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets. The data generator models three types of relations in produced synthetic data: clustering of data, correlations of entities, and random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes. The LDBC designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).

\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}. The generator is designed to receive a vocabulary as an input  and supports two statistical distribution techniques for generating entities: Gaussian distribution and Zipf's power-law distribution. LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statement by assigning invalid domain and creating instances with no type information. The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets. The datasets can be generated in any of of two modes: on-disk and streaming.

### 2018-09-11 generators_general.tex
Minor corrections

First of all we will focus on papers dealing with generation of general graph
data not aiming at particular application domain. Currently, there exists a
number of tools which involve a kind of general graph data generator, such as
gtools from projects nauty and Traces~\cite{gtools} or the Stanford
GraphBase~\cite{GraphBase}. We will, however, focus on primarily
generating/benchmarking projects targeting Big Data world.

\paragraph {Preferential Attachment} Barabasi and Albert introduced a graph generation model that relies on two main mechanisms~\cite{Barabasi99emergenceScaling}. The first mechanism is continuously expanding the graphs by adding new vertices. The second mechanism is to preferentially attach the new vertices   to the nodes/regions that are already well connected. In this approach, the generation of large graphs is governed by standard, robust self-organizing mechanism that go beyond the characteristics of individual applications.

\paragraph {R-Mat} (\emph{R}ecursive \emph{Mat}rix) R-Mat is a procedural synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}. 
The generator is recursive and uses only a small number of parameters.
In principle, the strategy of this generator to find simple mechanisms to generate graphs that match
the properties of the real graphs. In particular, the design goals of R-Mat is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter. R-Mat can generate weighted, directed and bipartite graphs.

\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on size of the
database of graphs, their average size and average density, the authors have
also implemented a synthetic generator called GraphGen~\cite{GraphGen}. It is
based on the IBM synthetic data generation code for associations and sequential
patterns\footnote{From 1996, no longer available at
\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
mining/mining.shtml}.}. GraphGen creates a collection of labeled, undirected and
connected graphs aiming at performance evaluation of frequent subgraph mining
algorithms and graph query processing algorithms. The result is represented as a
list of graphs, each consisting of a list of nodes and a list of edges.

\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
a scalable data generator which produces weighted, undirected graph as a list of
edge tuples containing the label of start vertex and end vertex together with a
weight that represents data assigned to the edge. The space of vertex  labels is
the set of integers beginning with 0. The input values required to describe the
graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
(i.e., half the average degree of a vertex in the graph). The graph generator is
a Kronecker generator similar to R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}. The data must not exhibit any locality,
so in the final step the vertex labels and order of edges are randomly shuffled.
The covered operations currently involve BFS; however, the authors intend to
involve also two more types -- optimization (single source shortest path) and
edge-oriented (maximal independent set) -- and five graph-related business areas
cybersecurity, medical informatics, data enrichment, social networks, and
symbolic networks.

\paragraph{BTER} BTER (Block Two-Level
Erd\"{o}-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
probabilities, connected randomly between them. As a main feature, BTER is able
to reproduce input degree distributions and average clustering
coefficient per degree values. The generators starts by grouping the vertices
by degree $d$, and forming groups of size $d+1$ degree $d$ nodes. Then, these
groups are assigned an internal edge probability in order to match the observed
average clustering coefficient of the nodes of such degree. Based on this
probability, for each node, the excess degree is computed (the degree that in
expectation will not be realized internally in the group) and used to connect
nodes from different groups at random. The authors describe a highly scalable
MapReduce based implementation that is capable of generating large graphs (with
billions of nodes) in reasonable amounts of time.

\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
designed to run on Vertex Centric computing frameworks like
Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
additional feature that it is more accurate when reproducing the clustering
coefficient of the input graph. Instead of just focusing on the average
clustering coefficient for each degree, Darwini is able to model the clustering
coefficient distribution per degree. It achieves this by grouping the vertices
of the graph into buckets by the expected number of closed triangles they need
to close in order to attain the their expected clustering coefficient, which is
sampled from the input distributions. Then, the vertices in each bucket are
connected randomly with a probability that would produce, in expectation, the
desired number of triangles for such bucket. Then, as in BTER, the excess degree
is used to connect the different buckets. The authors report that Darwini is
able to generate graphs with billions and even trillions of edges.

>>>>

First of all we focus on papers dealing with generation of general graph
data not aiming at a particular application domain. Currently, there exists a
number of tools which involve a kind of general graph data generator, such as
gtools from projects nauty and Traces~\cite{gtools} or the Stanford
GraphBase~\cite{GraphBase}. We, however, focus on primarily
generating/benchmarking projects targeting Big Data world.

\paragraph {Preferential Attachment} Barabasi and Albert~\cite{Barabasi99emergenceScaling} introduced a graph generation model that relies on two main mechanisms. The first mechanism is continuously expanding the graphs by adding new vertices. The second mechanism is to preferentially attach the new vertices   to the nodes/regions that are already well connected. So, in this approach, the generation of large graphs is governed by standard, robust self-organizing mechanisms that go beyond the characteristics of individual applications.

\paragraph {R-Mat} (\emph{R}ecursive \emph{Mat}rix) R-Mat is a procedural synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
The generator is recursive and uses only a small number of parameters.
In principle, the strategy of this generator is to find simple mechanisms to generate graphs that match
the properties of the real graphs. In particular, the design goals of R-Mat is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter. R-Mat can generate weighted, directed and bipartite graphs.

\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
database of graphs, their average size and average density, the authors have
also implemented a synthetic generator called GraphGen~\cite{GraphGen}. It is
based on the IBM synthetic data generation code for associations and sequential
patterns\footnote{From 1996, no longer available at
\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
mining/mining.shtml}}. GraphGen creates a collection of labeled, undirected and
connected graphs aiming at performance evaluation of frequent subgraph mining
algorithms and graph query processing algorithms. The result is represented as a
list of graphs, each consisting of a list of nodes and a list of edges.

\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
a scalable data generator which produces weighted, undirected graph as a list of
edge tuples containing the label of start vertex and end vertex together with a
weight that represents data assigned to the edge. The space of vertex  labels is
the set of integers beginning with 0. The input values required to describe the
graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
(i.e., half the average degree of a vertex in the graph). The graph generator is
a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
so in the final step the vertex labels and order of edges are randomly shuffled.
The covered operations currently involve BFS; however, the authors intend to
involve also two more types -- optimization (single source shortest path) and
edge-oriented (maximal independent set) -- and five graph-related business areas:
cybersecurity, medical informatics, data enrichment, social networks, and
symbolic networks.

\paragraph{BTER} BTER (Block Two-Level
Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
probabilities, connected randomly between them. As the main feature, BTER is able
to reproduce input degree distributions and average clustering
coefficient per degree values. The generator starts by grouping the vertices
by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
groups are assigned an internal edge probability in order to match the observed
average clustering coefficient of the nodes of such degree. Based on this
probability, for each node, the excess degree (i.e, the degree that in
expectation will not be realized internally in the group) is computed and used to connect
nodes from different groups at random. The authors describe a highly scalable
MapReduce based implementation that is capable of generating large graphs (with
billions of nodes) in reasonable amounts of time.

\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
designed to run on Vertex Centric computing frameworks like
Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
additional feature that it is more accurate when reproducing the clustering
coefficient of the input graph. Instead of just focusing on the average
clustering coefficient for each degree, Darwini is able to model the clustering
coefficient distribution per degree. It achieves this by grouping the vertices
of the graph into buckets by the expected number of closed triangles they need
to close in order to attain the expected clustering coefficient, which is
sampled from the input distributions. Then, the vertices in each bucket are
connected randomly with a probability that would produce, in expectation, the
desired number of triangles for such bucket. Then, as in BTER, the excess degree
is used to connect the different buckets. The authors report that Darwini is
able to generate graphs with billions and even trillions of edges.
